### 2025-09-22 src/articles/article3.qmd
Fix glossary

1. The active chapter will meet once per week while school is in session, as required by International Bylaws (IBL) Article V, Section 7, Part A.
1. The default time for a chapter meeting will be Sunday at 6:30 PM unless legislated otherwise.

@@

1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the time specified by the Excuse Plan.
1. Excuses must be approved by a simple majority vote of Executive Council (EC).
1. Failure to attend a chapter meeting without an approved excuse (in accordance with Article III, Section B, Item 1) will count as an unexcused absence.

@@

1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary with the possibility of suspension.
1. A brother who has three unexcused absences throughout the semester will be staggard.
1. A brother who has four unexcused absences throughout the semester will be placed on probation until the end of the semester.
1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.

@@

1. All officer reports and communications must be submitted in writing to the Secretary prior to a chapter meeting at a time decided by the Secretary. Emergency reports or communications may be given at the discretion of the presiding officer.
1. No one will leave any chapter meeting unless excused by the presiding officer.
1. Any member whose conduct is unbecoming of a brother may be asked to leave the meeting by the presiding officer.
1. The First Guard will determine and enforce proper dress code at chapter meetings.
1. At the discretion of the First Guard, entrance to chapter meetings will be conducted according to Ritual.
1. No guests will be permitted on the first floor or basement of the house during a chapter meeting or the preparation thereof unless permitted by the chair.
1. There will be no food or drink, with the exception of water in a resealable container, at any chapter meeting, unless the First Guard declares otherwise.
1. Motions that call for a vote require a simple majority in order to be passed, unless the creator of the motion specifies otherwise.

>>>>

1. The active chapter will meet once per week while school is in session, as required by International Bylaws ({{< var acronyms.ibl >}}) Article V, Section 7, Part A.
1. The default time for a chapter meeting will be Sunday at 6:30 PM unless legislated otherwise.

@@

1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the time specified by the Excuse Plan.
1. Excuses must be approved by a {{< var glossary.simple-majority >}} vote of Executive Council ({{< var acronyms.ec >}}).
1. Failure to {{< var glossary.attend >}} a chapter meeting without an approved excuse (in accordance with Article III, Section B, Item 1) will count as an unexcused absence.

@@

1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary with the possibility of suspension.
1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.
1. A brother who has four unexcused absences throughout the semester will be placed on {{< var glossary.probation >}} until the end of the semester.
1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.

@@

1. All officer reports and communications must be submitted in writing to the Secretary prior to a chapter meeting at a time decided by the Secretary. Emergency reports or communications may be given at the discretion of the presiding officer.
1. No one will leave any chapter meeting unless excused by the presiding officer.
1. Any member whose conduct is unbecoming of a brother may be asked to leave the meeting by the presiding officer.
1. The First Guard will determine and enforce proper dress code at chapter meetings.
1. At the discretion of the First Guard, entrance to chapter meetings will be conducted according to Ritual.
1. No guests will be permitted on the first floor or basement of the house during a chapter meeting or the preparation thereof unless permitted by the chair.
1. There will be no food or drink, with the exception of water in a resealable container, at any chapter meeting, unless the First Guard declares otherwise.
1. Motions that call for a vote require a {{< var glossary.simple-majority >}} in order to be passed, unless the creator of the motion specifies otherwise.

### 2025-09-22 src/articles/article4.qmd
Fix glossary

1. All brothers eligible to vote must vote.
1. Only active brothers who are not on probation or financial probation are eligible to vote.
1. Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.
1. A brother not required to pay local dues is ineligible to vote.
1. Unless specified in Article IV, Section B, or explicitly voted on by simple majority, the method of voting will be by a counted show of hands.

@@

1. The following votes will be performed by ballot:
   a. New Members for Initiation
   b. Officer Elections
   c. To overturn an Executive Council (EC) Interpretation of the bylaws (Article I, Section D)
   d. At a suspension trial
   e. To retain a candidate who was not initiated the previous semester

1. Balloting
   a. The Second Guard and the Chaplain will collect and count the ballots.
   b. The chaplain will confirm the count and repeat the results to the presiding officer.
   c. No brother may count the ballots for a matter related to himself.
   d. In the case of absence, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the ballots.

1. New Members for Initiation
   a. Balloting on New Members for Initiation will be in accordance with the International Bylaws (IBL) of Theta Chi Fraternity, Article VI, Section 4, paragraph d.
   b. New Members must be approved by a ¾ vote of eligible voting members of the active chapter to be initiated.

1. Officer Elections
   a. Officers will be elected by simple majority vote.
   b. In the case that no nominee receives a simple majority, there will immediately be another vote between all candidates who received the two highest counts of votes.\
   c. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for CAB interviews.

>>>>

1. All brothers eligible to vote must vote.
1. Only active brothers who are not on {{< var glossary.probation >}} or {{< var glossary.financial-probation >}} are eligible to vote.
1. Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.
1. A brother not required to pay local dues is ineligible to vote.
1. Unless specified in Article IV, Section B, or explicitly voted on by {{< var glossary.simple-majority >}}, the method of voting will be by a counted show of hands.

@@

1. The following votes will be performed by ballot:
   a. New Members for Initiation
   b. Officer Elections
   c. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (Article I, Section D)
   d. At a suspension trial
   e. To retain a candidate who was not initiated the previous semester

1. {{< var glossary.ballot >}}ing
   a. The Second Guard and the Chaplain will collect and count the {{< var glossary.ballot >}}s.
   b. The chaplain will confirm the count and repeat the results to the presiding officer.
   c. No brother may count the {{< var glossary.ballot >}}s for a matter related to himself.
   d. In the case of absence, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the {{< var glossary.ballot >}}s.

1. New Members for Initiation
   a. {{< var glossary.ballot >}}ing on New Members for Initiation will be in accordance with the International Bylaws ({{< var acronyms.ibl >}}) of Theta Chi Fraternity, Article VI, Section 4, paragraph d.
   b. New Members must be approved by a ¾ vote of eligible voting members of the active chapter to be initiated.

1. Officer Elections
   a. Officers will be elected by {{< var glossary.simple-majority >}} vote.
   b. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.\
   c. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for {{< var acronyms.cab >}} interviews.
